Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-07-01 paper/src/6_conclusion.tex
several updates
modify 6_

\section{Conclusion and Future Work}

@@

From simulation result, we showed that our I/O burst buffer can increase I/O throughput when Internet throughput is far smaller than interconnection throughput as well as reducing the overall cost.

>>>>

\section{Conclusion}
\label{sec:conclusion}

@@

From simulation result, we showed that our I/O burst buffer can burst I/O throughput about 4-20 times depends on cache hit rate as well as reduce overall cost about 2-12 times when Internet throughput is far smaller than interconnection throughput.
